Refinements for open automata

### 2023-03-16 2021-Refinement/paper/refinementarticleV2.tex
proof

\RAB{The composition of the family of OTs $t_{3x}^{x\in X}$ originating from $s_3$ which are related $s_2$ with the same transitions of $A_1$ (modulo renaming) as one used to build $t_{12}$ produces a single transition $t_{13}$.} This is,
because the hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
\]

\RAB{Pourquoi masquer partie en dessous dans le latex?\\ we need to prove  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$}
% 
%$\forall x \in X$ we have
%\begin{align*}		
%J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
%& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
%& = \mpar{J'_{12}\cap H' }
%\end{align*}

We have by definition 
\[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
Thus, because transitions $t^1_1$ and  $t^2_1$ are the same:
\[R' \mpar{s_{12}, s_{13}} \implies
\underbrace{R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{R' \mpar{s'_{12}, s'_{13}}}
\]

@@

\RAB{Because $\alpha_{12}$ and $\alpha_{13}$ are the same, as well as  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), and by considering all the family of weak open transitions indexed over X starting from $s_{3}$ which are related with $s_{2}$, we deduce from the above the expected formula:}

%From the above we can deduce the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
\begin{array}{l}
			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
		\end{array}}   
\end{multline*}

>>>>

The hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in {J^{2}_1}'} }}{g^2_1}{\psi^2_1}
\]
We thus take $({t_{13 x}})^{x\in X} = \{t_{13}\}$.
$\forall x \in X$ we have $J'_{13x} =  {J^{2}_1}'$ and trivially:
\begin{align*}		
J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
& = \mpar{J'_{12}\cap H' }
\end{align*}

Moreover, we have by definition 
\[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
Thus, because transitions $t^1_1$ and  $t^2_1$ are the same:
\[R' \mpar{s_{12}, s_{13}} \implies
\underbrace{R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{R' \mpar{s'_{12}, s'_{13}}}
\]

@@

Because $\alpha_{12}$ and $\alpha_{13}$ are the same, and also  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), we deduce from the above the expected formula (instantiated with $X$ a singleton): %From the above we can deduce the expected formula:
\begin{multline*}
V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
\implies \hspace{10em}\\ %\operatorname*{\bigsymb{\bigvee}}_{x \in X}
 \mpar{\everymath{\displaystyle}
%\begin{array}{l}
			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
%		\end{array}
}   
\end{multline*}
